Fast approximate Bayesian inference for small-area estimation of HIV indicators using the Naomi model

### 2023-03-03 src/docs_paper/paper.Rmd
Some writing

Using one `TMB` C++ user-template (available in the appendix), we fit the simplified Naomi model (Section \ref{sec:naomi}) to data from Malawi using four inferential approaches: (1) EB combined with a Gaussian approximation using `TMB`, (2) AGHQ combined with a Gaussian approximation using `aghq`, (3) AGHQ combined with a Laplace approximation by extending `aghq` and (4) the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using `tmbstan`.
Further details regarding particular settings used for each inferential method are provided in Table \ref{tab:inference-methods}.

@@

We used three methods to assess the accuracy of posterior distributions produced by each inferential method as compared with those from NUTS: (1) Kolmogorov-Smirnov tests, (2) maximum mean discrepancy, and (3) Pareto-smoothed importance sampling.

>>>>

Using one `TMB` C++ user-template (available in the appendix), we fit the simplified Naomi model (Section \ref{sec:naomi}) to data from Malawi using four inferential approaches.
There were: (1) EB combined with a Gaussian approximation using `TMB`, (2) AGHQ combined with a Gaussian approximation using `aghq`, (3) AGHQ combined with a Laplace approximation by extending `aghq` and (4) the Hamiltonian Monte Carlo (HMC) algorithm No-U-Turn Sampling (NUTS) using `tmbstan`.
Particular settings used for each inferential method are provided in Table \ref{tab:inference-methods}.
For the deterministic methods, following inference we simulated hyperparameter and latent field samples.
Then, for all methods, we simulated model outputs.

@@

We used three methods to assess the accuracy of posterior distributions produced by each inferential method as compared with those from NUTS: (1) Kolmogorov-Smirnov tests, (2) maximum mean discrepancy, and (3) Pareto-smoothed importance sampling.
From an applied perspective, our main interest is in comparing the accuracy of model outputs, rather than the internal hyperparameters or latent field parameters.
That said, obtaining accurate inferences for these internal parameters is also of interest.
